Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
Discussion

>>>>

In a future work, this framework could be used for feature detection purposes
such as presented in \cite{SMI2015}. The point classification is done by computing
the curvature at different radii and comparing them. Using our framework,
this may be done in a real-time manner.
The computed curvature could also be used to control the refinement of the
triangulation. We are for now only using the normal computation for shading
purposes but we could imagine using it along with the vertices to do a
Poisson reconstruction of the object.
